Practical Effects of Integrating Temperature with Strang Split Reactions

### 2021-03-18 strang/paper.tex
fix abstract

%======================================================================
% Abstract and Keywords
%======================================================================
\begin{abstract}
For astrophysical reacting flows, operator splitting is commonly used
to couple hydrodynamics and reactions.  Each process operates
independent of one another, but by staggering the updates in a
symmetric fashion (via Strang splitting) second order accuracy in time
can be achieved.  However, approximations are often made to the
reacting system, including the choice of whether or not to integrate
temperature with the species.  Here we demonstrate through a simple
convergence test that integrating temperature together with reactions
achieves the best convergence when modeling reactive flows with Strang
splitting.
\end{abstract}

>>>>

%======================================================================
% Abstract and Keywords
%======================================================================
\begin{abstract}
For astrophysical reacting flows, operator splitting is commonly used
to couple hydrodynamics and reactions.  Each process operates
independent of one another, but by staggering the updates in a
symmetric fashion (via Strang splitting) second order accuracy in time
can be achieved.  However, approximations are often made to the
reacting system, including the choice of whether or not to integrate
temperature with the species.  Here we demonstrate through a simple
convergence test that integrating an energy equation together with reactions
achieves the best convergence when modeling reactive flows with Strang
splitting.
\end{abstract}
